Clicks and Cliques

### 2018-12-23 papersoul.Rnw
update order import.plot2 chunk

ggplot(data = aux, aes(x = fct_reorder(dim2, rmdg, max), y = QSB, fill = rmdg )) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 90, size = I(12)), axis.title.x = element_blank() )  + scale_fill_gradient(low = "white", high = "red") + theme(legend.position = 'none')

>>>>

a <- aux %>% select(QSB,dim2, rmdg) %>% spread(dim2,rmdg) %>% 
  select(-QSB) %>% cor()

cl <- abs(1-a) %>%  as.dist() %>% hclust( method = 'ward.D')

ggplot(data = aux, aes(x = fct_relevel(dim2, cl$labels[cl$order]), y = QSB, fill = rmdg )) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 90, size = I(12)), axis.title.x = element_blank() )  + scale_fill_gradient(low = "white", high = "red") + theme(legend.position = 'none')
